An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex
algorithm finish typeset, added last references

\begin{algorithm}[tb]
    \caption{Contour combination algorithm}
   \label{alg:overlap}
\begin{algorithmic}
    \STATE {\bfseries Input:}  $contour1$, $contour2$, $text$
    \STATE $xGap =$ calculateXaxisDistance $contour1$, $contour2$
    \STATE $yOverlap =$ calculateYoverlap $contour1$, $contour2$
    \STATE $avgWidth =$ getAverageWordWith $text$
    \IF{ 
    $xGap < avgWidth $ \\ $* (1 / (averageCharacterCount * 2))$ \\  {\bfseries and} \\ $yOverlap > min(contour1.height, contour2.height)$ \\ $*  requiredYaxisOverlap $ 
    }
    \STATE combineContours $contour1$ $contour2$
    \ENDIF
\end{algorithmic}
The chosen paramters are:
\\
$averageCharacterCount = 8$ 
\\
$requiredYaxisOverlap = 1/2$
\end{algorithm}

@@

\begin{algorithm}[tb]
   \caption{Algorithm for line reconstruction}
   \label{alg:linereconstr}
\begin{algorithmic}
   \STATE {\bfseries Input:} $extractedWords$, $textlines$
   \REPEAT
        \STATE $highestWord = findHighestWord $
        \STATE $newline = [highestWord]$
        \STATE Initialize $noChange = true$.
        \STATE $avgY= newline$.findAverageYpos
        \REPEAT
            \FOR{$word$ {\bfseries in} $extractedWords$}
            \STATE $boundRect = word.contour.boundingRect$
            \IF{ $avgY > word.y$ {\bfseries and} $avgY < word.y + word.h$ }
            \STATE $line$.add $word$
            \STATE $noChange = false$
            \ENDIF
        \ENDFOR
        \UNTIL{$noChange = true$}
        \STATE $textlines$.add $newline$
   \UNTIL{$words$.empty $= true$}
\end{algorithmic}
\end{algorithm}

@@

The text to word segmentation process can be improved upon and made more robust.
Advanced text segmentation approaches can be utilized to extract the text segments from documents containing images and other unwanted elements.
Algorithms that provide better noise reduction can be added to handle text images with more noise,
and experiments with rotations of the text can provide us with a more robust system to tackle text images containing heavily slanted text lines.

The character segmentation process is inadequate as it is, and generally unable to segment words adequately so that the character recognition step can recognise the found segments.
More postprocessing can be used through rule based filters and a more robust neural network to correct the found segmentation points, but this will never reach an optimal solution through rule based filters alone because of the ambiguity of this problem.

>>>>

\begin{algorithm}[tb]
    \caption{Contour combination algorithm}
   \label{alg:overlap}
\begin{algorithmic}
    \STATE {\bfseries Input:}  $contour1$, $contour2$, $text$
    \STATE $xGap =$ XAxisDistance $contour1$, $contour2$
    \STATE $yOverlap =$ YAxisOverlap $contour1$, $contour2$
    \IF{ 
    \\ 
    \hspace{8px} $xGap < text$.averageWordWith 
    \\
    \hspace{8px} $* $ \hspace{2px} $(1 / (averageCharacterCount * 2))$ 
    \\
    {\bfseries and} 
    \\ 
    \hspace{8px} $yOverlap > min(contour1.height, contour2.height)$ 
    \\
    \hspace{8px} $* $ \hspace{2px} $  requiredYaxisOverlap $ 
    }
    \vspace{4px}
    \STATE combineContours $contour1$ $contour2$
    \ENDIF
\end{algorithmic}
The chosen paramters are:
\\
$averageCharacterCount = 8$ 
\\
$requiredYaxisOverlap = 1/2$
\end{algorithm}

@@

\begin{algorithm}[tb]
   \caption{Algorithm for line reconstruction}
   \label{alg:linereconstr}
\begin{algorithmic}
   \STATE {\bfseries Input:} $extractedWords$, $textlines$
   \REPEAT
        \STATE $newline = [ $wordWithHighestYPosition$ ]$
        \STATE $avgY= newline$.averageYPosition
        \REPEAT
            \FOR{$word$ {\bfseries in} $extractedWords$}
            \STATE $boundRect = word.contour.boundingRect$
            \IF{ $avgY > word.y$ {\bfseries and} $avgY < word.y + word.h$ }
            \STATE $line$.add $word$
            \ENDIF
        \ENDFOR
        \UNTIL{NotChangedLastIteration $line$}
        \STATE $textlines$.add $newline$
   \UNTIL{$words$.empty $= true$}
\end{algorithmic}
\end{algorithm}

@@

The text to word segmentation process can be improved upon and made more robust.
More advanced text segmentation approaches can be utilized to extract the text segments from documents containing images and other unwanted elements. \cite{textsegm}
Algorithms that provide better noise reduction can be added to handle text images with more noise,
and experiments with rotations of the text can provide us with a more robust system to tackle text images containing heavily slanted text lines.

The character segmentation process is insufficient as it is, and generally unable to segment words adequately so that the character recognition step can recognise the found segments.
More postprocessing can be used through rule based techniques and a more robust neural network to correct the found segmentation points. \cite{segmtechniques}
